Probabilistic Catalogs from Crowded Star Fields

### 2012-09-25 paper/ms.tex
New figure -- inference from break2.txt
Lots of tidying

\abstract{We introduce a fully probabilistic method for producing catalogs
from images of crowded stellar fields. The method is demonstrated on simulated
data where the luminosity function of the stars is a broken power-law.}

\section{Introduction}

A fundamental problem in astronomy is the construction of {\it catalogs} from
raw image data. {\bf The catalogs are then used for...}
Standard tools for generating catalogs include \texttt{SExtractor}
\citep{sextractor}, {\bf more refs}.

@@

\section{Bayesian Inference}
To quantitatively model uncertainties, Bayesian Inference is the appropriate
framework \citep{cox, jaynes, caticha}. Suppose there exist unknown parameters
(denoted
collectively by $\theta$) and we expect to obtain some data $x$. Our prior
state of knowledge about the parameters is modelled by a prior
probability distribution:
\begin{equation}
p(\theta)
\end{equation}
We also model how the parameters give rise to the data, via a generative model.
This is also known as a {\it sampling distribution}.
\begin{equation}
p(x|\theta)
\end{equation}
Despite the singular, the sampling distribution is actually a family of
probability distributions over the data space, one for each possible value
of $\theta$. Note that
the sampling distribution is also an assertion of a prior state of knowledge:
It models prior information about the fact that the data $x$ is connected to
the parameters $\theta$ in some way. Without this prior knowledge, learning is
impossible: there has to be some relationship between the parameters and the
data, otherwise new data tells you about nothing but itself.

@@

\subsection{The Hypothesis Space and the Prior}
Our model makes the following assumptions. There are an unknown number of stars
$N$ in the field. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
describe distribution of fluxes (commonly known as the {\it luminosity
function}) of the stars by parameters $\beta$. In summary, the unknown
parameters are:
\begin{eqnarray}
\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}
The prior probability distribution for the unknown parameters can be factorized
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\beta)\prod_{i=1}^N p(x_i, y_i)
p(f_i | \beta) 
\end{eqnarray}
Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the fluxes of the stars come independently from
a common distribution. If we knew the luminosity
function of the stars, then the location and flux of a particular star would
not tell us anything about the location and flux of another star. Really, this
is just a way of implementing exchangeability of the stars.

@@

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data; it describes the probability distribution we would use
to predict the data if we happened to know the true catalog. In our case,
the data will be an $n \times n$ array of pixel intensities:
\begin{eqnarray}
\{Y_{ij}\}
\end{eqnarray}
The center of each pixel is:
\begin{eqnarray}
\{x_{ij}, y_{ij}\}.
\end{eqnarray}
Thus, we need
a prescription for simulating an image $\{Y_{ij}\}$ from a catalog
$\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}$.
If we knew the true catalog, we could compute the
``mock image'' we would expect to see
in the absence of noise. This mock image (at infinite resolution) is given by:
\begin{eqnarray}
\mathcal{M}(x, y) &=& \sum_{i=1}^N \mathcal{P}(x - x_i, y - y_i)
\end{eqnarray}
where $\mathcal{P}$ is the pixel-convolved point spread function (PSF).
Throughout this paper we
assume the pixel-convolved PSF is a known weighted mixture of two concentric
circular
Gaussians with widths $s_1$ and $s_2$:
\begin{eqnarray}
\mathcal{P}(x, y) = \frac{w}{2\pi s_1^2}\exp
\left[
-\frac{1}{2s_1^2}\left(x^2 + y^2\right)
\right]
+ \frac{1-w}{2\pi s_2^2}\exp
\left[-\frac{1}{2s_2^2}\left(x^2 + y^2\right)
\right].
\end{eqnarray}
The finite-resolution observed image is assumed to be generated from the mock
image (evaluated at the center of each pixel) plus Gaussian noise:
\begin{eqnarray}
Y_{ij} &=& \mathcal{M}(x_{ij}, y_{ij}) + \epsilon_{ij}
\end{eqnarray}
where the errors $\{\epsilon_{ij}\}$ are independent and normally distributed:
\begin{eqnarray}
\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2).
\end{eqnarray}
Throughout this paper, we will assume that the noise variance $\sigma^2$ is
known. This is not usually true in practice (although it is often assumed).
However it is straightforward to extend the model so that $\sigma$ is an
unknown parameter.

\subsection{The Prior Distribution}
The prior distribution for the number of stars $N$ is uniform between 0 and
some maximum number $N_{\rm max}$. The extent of the image is assumed to be
from $x=-1$ to $x=1$ and from $y=-1$ to $y=1$ in arbitrary units, and the
positions of the stars are assigned independent uniform priors:
\begin{eqnarray}
x_i &\sim& \textnormal{Uniform}(-1.1, 1.1) \\
y_i &\sim& \textnormal{Uniform}(-1.1, 1.1) \\
\end{eqnarray}
The model for the luminosity function is a broken power-law with four
parameters:
\begin{eqnarray}
\beta = \{h_1, h_2, \alpha_1, \alpha_2\}.
\end{eqnarray}

\section{MCMC Implementation}
The sampling was implemented using the Diffusive Nested Sampling \citep{dnest}
method (hereafter DNS). DNS is based on the Metropolis-Hastings algorithm and
is very generally applicable. The main difference between DNS and the standard
Metropolis-Hastings algorithm is that the target distribution is modified.
Rather than simply exploring the posterior distribution over catalog space,
DNS constructs an alternative target distribution which is a mixture of the
prior distribution with more constrained versions of the prior distribution.
The modified target distribution assists

Nested Sampling is good because it is invariant under monotonic transformations
of the likelihood function. i.e. the exploration only depends on things like
whether one point is better than another, and not on how much better it is.

\section{A More Realistic Model}
\citep{2008ApJ...682..874K}

\section{Three Scenarios: Sparse, Cluster, and Crowded}
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

\begin{table}
\begin{center}
\begin{tabular}{ccccc}
Test Case & Parameter & Value \\
\hline
\sparse \\
\cluster \\
\crowded
\end{tabular}
\end{center}
\end{table}

\begin{figure}
\hspace{-1cm}
\includegraphics{Figures/test_cases.eps}
\end{figure}

\subsection{Sparse}
Sparse has a giant first-order phase transition. {\bf Nested Sampling is
mandatory!} Show the plot of it

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{Figures/likelihood.eps}
\end{center}
\end{figure}

\subsection{Cluster}
Was generated from non-uniform spatial distribution (obviously) but modelled
with a uniform one.

\subsection{Crowded}
Crowded is slow if the data have high S/N. Something like $e^5000$ compressions
are needed. Can do NS and not worry about equilibration if you are willing to
make a guess about the logXs of the levels.

\subsection{Toy Model}
For the first implementation I wrote at NYU, I used the following model and
priors:
\begin{itemize}
\item $N \sim \textnormal{Uniform}(0, 1, 2, ..., 1000)$ \\
\item The parameters of the spatial
distribution: $\alpha = \left\{x_c, y_c, \sigma\right\}$ \\
\item The spatial distribution: $p(x_i, y_i | \alpha)\sim\mathcal{N}\left(
\texttt{mean}=(x_c, y_c), \texttt{covariance}=
\left(\begin{array}{cc}\sigma^2 & 0 \\ 0 & \sigma^2\end{array}\right)\right)$ \\
\item Prior on $\alpha$: Uniform within image for $(x_c, y_c)$, logUniform for
$\sigma$ with max value $\sim$ image size.
\item The luminosity function: $p(f_i | \beta) \sim
\textnormal{Exponential}\left(\texttt{mean}=\beta\right)$ \\
\item Prior on $\beta$: logUniform with generous bounds.
\end{itemize}

\section{Acknowledgements}
BJB would like to thank his teaching mentor Dr Wayne Stewart.
Marshall, Lang, ...

@@

\section{Broken Power-Law Distribution}
The broken power-law distribution is defined by:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
The free parameters of the broken power-law are:
\begin{eqnarray}
\beta = \{x_1, x_2, \alpha_1, \alpha_2\}
\end{eqnarray}

@@

The second condition is the total probability must be 1:

@@

\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation. Consider a pixel.
The true flux $F$ within the pixel is:
\begin{eqnarray}
F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
pixel.

@@

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$(\alpha, \beta)$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Move stars along with $\alpha$
\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Stars fixed, use logHastings
factor \\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, use
logHastings factor \\
$(x,y)$ & $(x,y) \to (x,y)+(\delta_x, \delta_y)$ & Can move $>1$ star.
Include prior via logH \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes. Include prior
via logH
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.\label{proposals}}
\end{table}

@@

@@

>>>>

\abstract{We introduce a fully probabilistic method for producing catalogs
from images of crowded stellar fields. The feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainty.}

\section{Introduction}
A fundamental problem in astronomy is the construction of {\it catalogs} from
raw image data. {\bf The catalogs are then used for...}
Standard tools for generating catalogs include \texttt{SExtractor}
\citep{sextractor}, {\bf more refs}.

@@

\section{Bayesian Inference}
To quantitatively model uncertainties, Bayesian Inference is the appropriate
framework \citep{cox, jaynes, caticha}. Suppose there exist unknown parameters
(denoted
collectively by $\theta$) and we expect to obtain some data $x$. Our prior
state of knowledge about the parameters is modelled by a prior
probability distribution:
\begin{equation}
p(\theta)
\end{equation}.
Note that this is a very concise notation \citep{hogg}.
We also model how the parameters give rise to the data, via a generative model.
This is also known as a {\it sampling distribution}.
\begin{equation}
p(x|\theta)
\end{equation}
Despite the singular, the sampling distribution is actually a family of
probability distributions over the data space, one for each possible value
of $\theta$. Note that
the sampling distribution is also an assertion of a prior state of knowledge:
It models prior information about the fact that the data $x$ is connected to
the parameters $\theta$ in some way. Without this prior knowledge, learning is
impossible: there has to be some relationship between the parameters and the
data, otherwise new data tells you about nothing but itself.

@@

\subsection{The Hypothesis Space and the Prior}
Our model makes the following assumptions. There are an unknown number of stars
$N$ in the field. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
describe the distribution of fluxes (commonly known as the {\it luminosity
function}) of the stars by parameters $\beta$. In summary, the unknown
parameters are:
\begin{eqnarray}
\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}
The prior probability distribution for the unknown parameters can be factorized
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\beta)\prod_{i=1}^N p(x_i, y_i)
p(f_i | \beta) 
\end{eqnarray}
Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the fluxes of the stars come independently from
a common distribution. If we knew the luminosity
function of the stars, then the location and flux of a particular star would
not tell us anything about the location and flux of another star. Really, this
is just a way of implementing exchangeability of the stars.

@@

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data; it describes the probability distribution we would use
to predict the data if we happened to know the true catalog. In our case,
the data will be an $n \times n$ array of pixel intensities:
\begin{eqnarray}
\{Y_{ij}\}
\end{eqnarray}
The center of each pixel is:
\begin{eqnarray}
\{x_{ij}, y_{ij}\}.
\end{eqnarray}
Thus, we need
a prescription for simulating an image $\{Y_{ij}\}$ from a catalog $\theta$:
\begin{eqnarray}
\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}.
\end{eqnarray}
If we knew the true catalog, we could compute the
``mock image'' we would expect to see
in the absence of noise. This mock image (at infinite resolution) is given by:
\begin{eqnarray}
\mathcal{M}(x, y) &=& \sum_{i=1}^N \mathcal{P}(x - x_i, y - y_i)
\end{eqnarray}
where $\mathcal{P}$ is the pixel-convolved point spread function (PSF).
Throughout this paper we
assume the pixel-convolved PSF is a known weighted mixture of two concentric
circular
Gaussians with widths $s_1$ and $s_2$:
\begin{eqnarray}
\mathcal{P}(x, y) = \frac{w}{2\pi s_1^2}\exp
\left[
-\frac{1}{2s_1^2}\left(x^2 + y^2\right)
\right]
+ \frac{1-w}{2\pi s_2^2}\exp
\left[-\frac{1}{2s_2^2}\left(x^2 + y^2\right)
\right].
\end{eqnarray}
The finite-resolution observed image is assumed to be generated from the mock
image (evaluated at the center of each pixel) plus Gaussian noise:
\begin{eqnarray}
Y_{ij} &=& \mathcal{M}(x_{ij}, y_{ij}) + \epsilon_{ij}
\end{eqnarray}
where the errors $\{\epsilon_{ij}\}$ are independent and normally distributed:
\begin{eqnarray}
\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2).
\end{eqnarray}
Throughout this paper, we will assume that the noise variance $\sigma^2$ is
known. This is not usually true in practice (although it is often assumed).
However it is straightforward to extend the model so that $\sigma$ is an
unknown parameter or that the noise variance should be a function of the
intensity of the mock image \citep[e.g.][]{2011MNRAS.412.2521B}.

For the generation of the simulated data in Section~\ref{sec:simulated_data},
the values of the PSF parameters used were $s_1=0.02$, $s_2=0.1$ (one and
five pixel widths respectively), and $w=0.5$.

\subsection{The Prior Distribution}
The prior distribution for the number of stars $N$ is assigned to be uniform between 0 and
some maximum number $N_{\rm max}$. The extent of the image is assumed to be
from $x=-1$ to $x=1$ and from $y=-1$ to $y=1$ in arbitrary units, and the
positions of the stars are assigned independent uniform priors:
\begin{eqnarray}
x_i &\sim& \textnormal{Uniform}(-1.1, 1.1) \\
y_i &\sim& \textnormal{Uniform}(-1.1, 1.1) \\
\end{eqnarray}
The model for the luminosity function is a broken power-law with four
free parameters:
\begin{eqnarray}
\beta = \{h_1, h_2, \alpha_1, \alpha_2\}.
\end{eqnarray}
where $h_1$ is the lower flux cutoff, $h_2$ is a break-point, $\alpha_1$ is
the slope of the distribution between $h_1$ and $h_2$, and $\alpha_2$ is the
slope of the distribution above $h_2$. For details on the broken power-law
model, see Appendix~\ref{power_law}. The prior distribution on $h_1$, $h_2$,
$\alpha_1$ and $\alpha_2$ is assigned to be:
\begin{eqnarray}
\log h_1 &\sim& \textnormal{Uniform}(\log(10^{-3}), \log(10^{+3})) \\
\log h_2 &\sim& \textnormal{Uniform}(h_1, h_1 + 2.3) \\
\alpha_1 &\sim& \textnormal{Uniform}(1, 5) \\
\alpha_2 &\sim& \textnormal{Uniform}(1, 5).
\end{eqnarray}

This simply-parameterised model for the luminosity function can be criticised
on the basis that information from bright stars can be used to infer the
parameters of the luminosity function which then still apply at lower flux
levels. In principle, this can be resolved by using a more flexible distribution
\citep[e.g.][]{2008ApJ...682..874K} where each star's measured brightness
affects the inference of the luminosity function locally but not globally.

\section{MCMC Implementation}
The sampling was implemented using the Diffusive Nested Sampling \citep{dnest}
method (hereafter DNS). DNS is based on the Metropolis-Hastings algorithm and
is very generally applicable. The main difference between DNS and the standard
Metropolis-Hastings algorithm is that the target distribution is modified.
Rather than simply exploring the posterior distribution over catalog space,
DNS constructs an alternative target distribution which is a mixture of the
prior distribution with more constrained versions of the prior distribution.
The modified target distribution assists the sampling in several ways.
Firstly, the target distribution shrinks at a constant rate with time during the
initial phase of the exploration. This is similar to the popular ``simulated
annealing'' method but with an optimal annealing schedule. Secondly,
communication with the prior is maintained: once a catalog is found that
fits the data, the catalog can ``disintegrate'' back to the prior distribution
and re-fit, allowing different peaks in the parameter space to be explored
(if they exist). This all happens naturally within the context of a valid
MCMC sampler.

\section{Simulated Data}\label{sec:simulated_data}
We now apply the method to two illustrative simulated images generated from
the above model. The true parameter values used are listed in
Table~\ref{tab:truth}.
Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars and the second image contains $\sim$1000 stars. The images
are shown in Figure~\ref{fig:simulated_data}.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Test Case & Parameter & Value \\
\hline
1 & $N$ & 100\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.05\\
\hline
2 & $N$ & 1000\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.3\\
\hline
\end{tabular}
\end{center}
\caption{True parameter values used to generate the simulated data.
\label{tab:truth}}
\end{table}

\begin{figure}
\hspace{-1cm}
\includegraphics{Figures/test_cases.eps}
\caption{Two simulated images.
{\bf Left}: A field containing $\sim$100 stars.
{\bf Right}: A field containing $\sim$1000 stars.\label{fig:simulated_data}}
\end{figure}

\subsection{Test Case 1}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference1.eps}
\end{center}
\caption{Inference about the parameters for test case 1.\label{fig:results1}}
\end{figure}

{\bf Show phase transition}\\
{\bf Comment on computational speed}\\
{\bf Show a few catalogs}\\
{\bf Show posterior expected true scene}\\

\subsection{Test Case 2}
{\bf Show inference on parameters}\\
{\bf Show phase transition}\\
{\bf Comment on computational speed}\\
{\bf Show a few catalogs}\\
{\bf Show posterior expected true scene}\\

\section{Conclusions}
We can do it. This is important because...

\section{Acknowledgements}
Marshall, Lang, Geraint, Wayne Stewart...

@@

\section{Broken Power-Law Distribution}\label{power_law}
The broken power-law distribution is based on a straightforward extension
to a simple power-law distribution (also known as a Pareto distribution,
particularly in the statistics literature).
The broken power-law distribution for a variable $x$ is defined by:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
The free parameters of the broken power-law are:
\begin{eqnarray}
\beta = \{x_1, x_2, \alpha_1, \alpha_2\}
\end{eqnarray}

@@

The second condition is that the total probability must be 1:

@@

\section{Pixel Convolved PSF}
{\bf Do people need to be schooled on this? I did...}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation. Consider a pixel.
The true flux $F$ within the pixel is:
\begin{eqnarray}
F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
pixel.

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$\beta$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, put extra
term in acceptance probability \\
$(x_i,y_i)$ & $(x_i,y_i) \to (x_i,y_i)+(\delta_x, \delta_y)$ & Can move $>1$ star
in a single step \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes in a single step\\
\hline
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.\label{proposals}}
\end{table}

@@

\bibitem[Brewer et al.(2011)]{2011MNRAS.412.2521B} Brewer, B.~J., Lewis, 
G.~F., Belokurov, V., Irwin, M.~J., Bridges, T.~J., Evans, N.~W.\ 2011.\ 
Modelling of the complex CASSOWARY/SLUGS gravitational lenses.\ Monthly 
Notices of the Royal Astronomical Society 412, 2521-2529

@@

\bibitem[Hogg(2012)]{hogg} Hogg, D.~W.\ 2012.\ Data analysis 
recipes: Probability calculus for inference.\ ArXiv e-prints 
arXiv:1205.4446.
